---
title: "Gut Content Analysis: Amundsen graphs"
author: "Jess Madden"
date: "2/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(here)
library(readxl)
library(janitor)
library(lubridate)
library(broom)
library(effsize)
library(car)
library(kableExtra)
library(ggbeeswarm)
```

```{r}
gut_contents_all <- read.csv(here("data", "Diet_gutcontent_data.csv"))
seine_data <- read.csv(here("data", "Diet_seine_data.csv"))

gut_contents <- gut_contents_all %>% 
  clean_names()

```

### Guts summary

```{r}


guts <- gut_contents %>% 
  filter(count >0) %>% 
  group_by(site, season) %>% 
  summarise("Stomachs processed" = n_distinct(fish_id)) %>% 
  mutate(site_season = paste(site, season))

fish <- seine_data %>%
  filter(common_name == "Barred surfperch") %>% 
  filter(gut_collected == "Yes") %>% 
  filter(site %in% c("Percos", "Refugio", "R Beach")) %>%
  filter(season %in% c("Summer", "Fall")) %>% 
  group_by(site, season) %>% 
  summarise("Total collected" = n_distinct(fish_id)) %>% 
  mutate(site_season = paste(site, season))

guts_summary <- guts %>% 
  left_join(fish) %>% 
  select(site, season, "Stomachs processed", "Total collected")

guts_summary %>% 
  kbl() %>% 
  kable_styling()
```



### Amundsen plots

Frequency of occurrence of prey i: %Fi = (Ni/N)*100
Prey specific abundance: %Pi = (sum(Si)/sum(Sti)*100)

```{r}
# Frequency of occurrence by site

##### CHECK HERE THAT THERE ARE NO DUPLICATE GUT ITEMS
check_N_i <- gut_contents %>% 
  mutate(fish_id_id = paste(fish_id, id, sep = "_")) %>% 
  get_dupes(fish_id_id)


N_i <- gut_contents %>% 
  group_by(site) %>% 
  count(id) %>% 
  rename("N_i" = "n")

N_guts <- gut_contents %>% 
  group_by(site) %>% 
  summarize(n_distinct(fish_id))

#calculate %Fi

F_i <- N_i %>% 
  full_join(N_guts) %>% 
  rename("N_guts" = "n_distinct(fish_id)") %>% 
  mutate(F_i = ((N_i/N_guts)*100))
```

```{r}
# Prey-specific abundance

S_i <- gut_contents %>% 
  group_by(site, id) %>%
  summarise(S_i = sum(count))

#S_t_emerita

emerita_fish <- gut_contents %>% 
  filter(id == "Emerita analoga") %>% 
  select(fish_id) %>% 
  pull(fish_id) #vectorizes the list of fish guts that had emerita in them

S_t_emerita <- gut_contents %>%
  filter(fish_id %in% emerita_fish) %>% 
  group_by(site) %>%
  summarise(S_ti = sum(count))



#Calculate S_ti for each species

species_list <- unique(gut_contents$id)

S_ti <- data.frame()
for (spp in species_list){
  fish <- gut_contents %>% filter(id == spp) %>% select(id, fish_id)
  sum_t <- gut_contents %>% filter(fish_id %in% fish$fish_id) %>% group_by(site) %>% summarise(S_ti = sum(count))
  dat <- sum_t %>% mutate(species = spp)
  S_ti <- rbind.data.frame(S_ti, dat)
}

#calculate %Pi

S_i <- S_i %>% 
  mutate(site_id = paste(site, id, sep = "_"))

S_ti <- S_ti %>% 
  mutate("site_id" = paste(site, species, sep = "_"))

P_i <- S_i %>% 
  full_join(S_ti) %>% 
  select(site, id, S_i, S_ti) %>% 
  mutate(P_i = ((S_i/S_ti)*100))
```

Plot emerita 

```{r}
emerita <- F_i %>% 
  full_join(P_i) %>% 
  filter(id == "Emerita analoga")
  
ggplot(emerita, aes(x = F_i, y = P_i)) +
  geom_point() +
  facet_wrap(~site) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100)) +
  scale_y_continuous(limits = c(0, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", y = "% Prey-specific abundance")

```

### Amundsen plots: Lifestage comparison


Frequency of occurrence of prey i: %Fi = (Ni/N)*100
Prey specific abundance: %Pi = (sum(Si)/sum(Sti)*100)

```{r}
# Frequency of occurrence by life stage

gut_contents_ls <- gut_contents %>% 
  filter(lifestage %in% c("Adult", "Juvenile")) %>% 
  subset(taxa != "Urchin" & taxa != "Parasite" & taxa != "NA" & taxa != "Algae/Phyllo" & taxa != "Unidentified") #removed Urchin, PArasite, Unidentified, and NA

gut_contents_ls_summary <- gut_contents_ls %>% 
  group_by(site, season, lifestage) %>% 
  summarise(n = n_distinct(fish_id))

gut_contents_ls_summary %>% 
  kbl() %>% 
  kable_styling()

##### CHECK HERE THAT THERE ARE NO DUPLICATE GUT ITEMS
check_N_i <- gut_contents_ls %>% 
  mutate(fish_id_id = paste(fish_id, id, sep = "_")) %>% 
  get_dupes(fish_id_id)


N_i_ls <- gut_contents_ls %>% 
  group_by(site, lifestage) %>% 
  count(taxa) %>% 
  rename("N_i_ls" = "n")

N_guts_ls <- gut_contents_ls %>% 
  group_by(site, lifestage) %>% 
  summarize(n_distinct(fish_id))

#calculate %Fi

F_i_ls <- N_i_ls %>% 
  full_join(N_guts_ls) %>% 
  rename("N_guts_ls" = "n_distinct(fish_id)") %>% 
  mutate(F_i_ls = ((N_i_ls/N_guts_ls)*100))
```

```{r}
# Prey-specific abundance

S_i_ls <- gut_contents_ls %>% 
  group_by(site, lifestage, taxa) %>%
  summarise(S_i_ls = sum(count)) %>% 
  mutate(lifestage_id = paste(site, lifestage, taxa, sep = "_"))

#Calculate S_ti for each species

taxa_list <- unique(gut_contents_ls$taxa)

S_ti_ls <- data.frame()
for (i in taxa_list){
  fish <- gut_contents_ls %>% filter(taxa == i) %>% select(taxa, fish_id)
  sum_t <- gut_contents_ls %>% filter(fish_id %in% fish$fish_id) %>% group_by(site, lifestage) %>% summarise(S_ti_ls = sum(count))
  dat <- sum_t %>% mutate(taxa = i) %>% mutate(lifestage_id = paste(site, lifestage, taxa, sep = "_"))
  S_ti_ls <- rbind.data.frame(S_ti_ls, dat)
}

#calculate %Pi

P_i_ls <- S_i_ls %>% 
  full_join(S_ti_ls) %>% 
  select(site, lifestage, taxa, S_i_ls, S_ti_ls) %>% 
  mutate(P_i_ls = ((S_i_ls/S_ti_ls)*100))
```


Amundsen plots by lifestage 

```{r}
amundsen_ls <- F_i_ls %>% 
  full_join(P_i_ls) 

gut_contents_ls$site <- as.factor(gut_contents_ls$site)
gut_contents_ls$lifestage <- as.factor(gut_contents_ls$lifestage)

sample_size_ls <- gut_contents_ls %>% 
  group_by(lifestage) %>% 
  summarise(sample_size = n())
  
ggplot(amundsen_ls, aes(x = F_i_ls, y = P_i_ls, color=taxa)) +
  geom_point() +
  facet_grid(lifestage ~ site) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100)) +
  scale_y_continuous(limits = c(0, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", y = "% Prey-specific abundance")
```


### Amundsen plots: Seasonal comparison

#### All sites compiled

Frequency of occurrence of prey i: %Fi = (Ni/N)*100

Prey specific abundance: %Pi = (sum(Si)/sum(Sti)*100)

```{r}
# Frequency of occurrence by season

##### CHECK HERE THAT THERE ARE NO DUPLICATE GUT ITEMS
check_N_i <- gut_contents %>% 
  mutate(fish_id_id = paste(fish_id, id, sep = "_")) %>% 
  get_dupes(fish_id_id)

gut_contents <- gut_contents %>% 
  subset(taxa != "Urchin" & taxa != "Parasite" & taxa != "NA" & taxa != "Algae/Phyllo" & taxa != "Unidentified") #%>%  #removed Urchin, PArasite, Unidentified, and NA 
#  filter(lifestage == "Adult") ### REMOVES ADULTS FROM REST OF ANALYSES

N_i_ss <- gut_contents %>% 
  group_by(season) %>% 
  count(taxa, zone_trophic) %>% 
  rename("N_i_ss" = "n")

N_guts_ss <- gut_contents %>% 
  group_by(season) %>% 
  summarize(n_distinct(fish_id))

#calculate %Fi

F_i_ss <- N_i_ss %>% 
  full_join(N_guts_ss) %>% 
  rename("N_guts_ss" = "n_distinct(fish_id)") %>% 
  mutate(F_i_ss = ((N_i_ss/N_guts_ss)*100))
```

```{r}
# Prey-specific abundance

S_i_ss <- gut_contents %>% 
  group_by(season, taxa, zone_trophic) %>%
  summarise(S_i_ss = sum(count)) %>% 
  mutate(full_id = paste(season, taxa, sep = "_"))

#Calculate S_ti for each species

species_list <- unique(gut_contents$taxa)

S_ti_ss <- data.frame()
for (i in species_list){
  fish <- gut_contents %>% filter(taxa == i) %>% select(taxa, zone_trophic, fish_id)
  sum_t <- gut_contents %>% filter(fish_id %in% fish$fish_id) %>% group_by(season) %>% summarise(S_ti_ss = sum(count))
  dat <- sum_t %>% mutate(taxa = i) %>% mutate(full_id = paste(season, taxa, sep = "_"))
  S_ti_ss <- rbind.data.frame(S_ti_ss, dat)
}

#calculate %Pi

P_i_ss <- S_i_ss %>% 
  full_join(S_ti_ss) %>% 
  select(season, taxa, zone_trophic, S_i_ss, S_ti_ss) %>% 
  mutate(P_i_ss = ((S_i_ss/S_ti_ss)*100))
```


Amundsen plots by season

```{r, fig.width=10}
amundsen_ss <- F_i_ss %>% 
  full_join(P_i_ss)

amundsen_ss$season <- factor(amundsen_ss$season, levels = c("Summer", "Fall"))
amundsen_ss$zone_trophic <- factor(amundsen_ss$zone_trophic, levels = c("Beach kelp associated", "Beach suspension feeder", "Other beach", "Marine kelp associated", "Marine suspension feeder", "Other marine"))

sample_size_ss <- gut_contents %>% 
  group_by(season) %>% 
  summarise(sample_size = n_distinct(fish_id))

sample_size_ss %>% 
  kbl() %>% 
  kable_styling()
  
ggplot(amundsen_ss, aes(x = F_i_ss, y = P_i_ss, label = taxa)) +
  geom_point(size = 3, 
             aes(color=zone_trophic, shape=zone_trophic)) +
  facet_wrap(~season) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", 
       y = "% Prey-specific abundance"
       ) +
  scale_color_manual(values =  c("#C1C23C", "#C1C23C", "#C1C23C", "#0A6473", "#0A6473", "#0A6473")) +
  scale_shape_manual(values = c(16, 17, 3, 16, 17, 3))  +
  theme(panel.border = element_rect(size = .05, fill = NA), 
        panel.grid = element_blank(), 
        strip.text = element_text(size = 12), 
        legend.title = element_blank()) +  geom_text(check.overlap = TRUE)

```

### Amundsen plots: R Beach tide comparison


Frequency of occurrence of prey i: %Fi = (Ni/N)*100

Prey specific abundance: %Pi = (sum(Si)/sum(Sti)*100)

```{r}
# Frequency of occurrence by season

##### CHECK HERE THAT THERE ARE NO DUPLICATE GUT ITEMS
check_N_i <- gut_contents %>% 
  mutate(fish_id_id = paste(fish_id, id, sep = "_")) %>% 
  get_dupes(fish_id_id)

gut_contents_rb <- gut_contents %>% 
  subset(taxa != "Urchin" & taxa != "Parasite" & taxa != "NA" & taxa != "Algae/Phyllo" & taxa != "Unidentified") %>%  #removed Urchin, PArasite, Unidentified, and NA
  filter(site == "R Beach") %>% 
  filter(month == 7)
  
N_i_rb <- gut_contents_rb %>% 
  group_by(tide) %>% 
  count(taxa, zone_trophic) %>% 
  rename("N_i_rb" = "n")

N_guts_rb <- gut_contents_rb %>% 
  group_by(tide) %>% 
  summarize(n_distinct(fish_id))

#calculate %Fi

F_i_rb <- N_i_rb %>% 
  full_join(N_guts_rb) %>% 
  rename("N_guts_rb" = "n_distinct(fish_id)") %>% 
  mutate(F_i_rb = ((N_i_rb/N_guts_rb)*100))
```

```{r}
# Prey-specific abundance

S_i_rb <- gut_contents_rb %>% 
  group_by(tide, taxa, zone_trophic) %>%
  summarise(S_i_rb = sum(count)) %>% 
  mutate(full_id = paste(tide, taxa, sep = "_"))

#Calculate S_ti for each species

species_list <- unique(gut_contents_rb$taxa)

S_ti_rb <- data.frame()
for (i in species_list){
  fish <- gut_contents_rb %>% filter(taxa == i) %>% select(taxa, zone_trophic, fish_id)
  sum_t <- gut_contents_rb %>% filter(fish_id %in% fish$fish_id) %>% group_by(tide) %>% summarise(S_ti_rb = sum(count))
  dat <- sum_t %>% mutate(taxa = i) %>% mutate(full_id = paste(tide, taxa, sep = "_"))
  S_ti_rb <- rbind.data.frame(S_ti_rb, dat)
}

#calculate %Pi

P_i_rb <- S_i_rb %>% 
  full_join(S_ti_rb) %>% 
  select(tide, taxa, zone_trophic, S_i_rb, S_ti_rb) %>% 
  mutate(P_i_rb = ((S_i_rb/S_ti_rb)*100))

amundsen_rb <- F_i_rb %>% 
  full_join(P_i_rb)
```


```{r, fig.width=10}

amundsen_rb$tide <- factor(amundsen_rb$tide, levels = c("Spring", "Neap"))
amundsen_rb$zone_trophic <- factor(amundsen_rb$zone_trophic, levels = c("Beach kelp associated", "Beach suspension feeder", "Other beach", "Marine kelp associated", "Marine suspension feeder", "Other marine"))

sample_size_rb <- gut_contents_rb %>% 
  group_by(tide) %>% 
  summarise(sample_size = n_distinct(fish_id))

sample_size_rb %>% 
  kbl() %>% 
  kable_styling()
  
ggplot(amundsen_rb, aes(x = F_i_rb, y = P_i_rb, label = taxa)) +
  geom_point(size = 3, 
             aes(color=zone_trophic, shape=zone_trophic)) +
  facet_wrap(~tide) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", 
       y = "% Prey-specific abundance"
       ) +
  scale_color_manual(values =  c("#C1C23C", "#C1C23C", "#C1C23C", "#0A6473", "#0A6473", "#0A6473")) +
  scale_shape_manual(values = c(16, 17, 3, 16, 17, 3))  +
  theme(panel.border = element_rect(size = .05, fill = NA), 
        panel.grid = element_blank(), 
        strip.text = element_text(size = 12), 
        legend.title = element_blank()) +  geom_text(check.overlap = TRUE)

```
##### Tide comparison: gut richness

```{r}
gut_richness_rb <- gut_contents_rb %>% 
  group_by(tide, fish_id) %>% 
  summarise(richness = n_distinct(diversity))

gut_richness_rb_summary <- gut_richness_rb %>% 
  group_by(tide) %>% 
  summarise(avg = mean(richness), 
            se = sd(richness)/sqrt(n()), 
            n = n())

ggplot(gut_richness_rb_summary, aes(x = tide, y = avg, fill = tide)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymax = avg+se, 
                    ymin = avg-se), 
                width = 0.1) +
    theme_minimal() + 
  scale_fill_manual("legend", values = c("#BBA5B7", "#657A85")) +
  theme(legend.position = "none") +
  xlab("") +
  ylab("") +
  theme(axis.line =  element_line(size = .05), 
        panel.grid = element_blank())
```


#### Amundsen plots: Site comparison

Figure out which taxa are dominant (average abundance >2%)

Frequency of occurrence of prey i: %Fi = (Ni/N)*100
Prey specific abundance: %Pi = (sum(Si)/sum(Sti)*100)

```{r}
#calculate average % abundance

gut_totals <- gut_contents %>% 
  group_by(fish_id) %>% 
  summarise(total_gut_content = sum(count))

avg_percent_abund <- gut_contents %>% 
  full_join(gut_totals) %>% 
  mutate(percent_abundance = (count/total_gut_content)*100) %>% 
  group_by(taxa) %>% 
  summarise(Pi = mean(percent_abundance))

```

```{r}
# Frequency of occurrence by site

##### CHECK HERE THAT THERE ARE NO DUPLICATE GUT ITEMS
check_N_i <- gut_contents %>% 
  mutate(fish_id_id = paste(fish_id, id, sep = "_")) %>% 
  get_dupes(fish_id_id)


N_i <- gut_contents %>% 
  group_by(site) %>% 
  count(taxa) %>% 
  rename("N_i" = "n")

N_guts <- gut_contents %>% 
  group_by(site) %>% 
  summarize(n_distinct(fish_id))

#calculate %Fi

F_i <- N_i %>% 
  full_join(N_guts) %>% 
  rename("N_guts" = "n_distinct(fish_id)") %>% 
  mutate(F_i = ((N_i/N_guts)*100))
```

```{r}
# Prey-specific abundance

S_i <- gut_contents %>% 
  group_by(site, taxa, zone_trophic) %>%
  summarise(S_i = sum(count))

#Calculate S_ti for each family

taxa_list <- unique(gut_contents$taxa)

S_ti <- data.frame()
for (i in taxa_list){
  fish <- gut_contents %>% filter(taxa == i) %>% select(taxa, zone_trophic, fish_id)
  sum_t <- gut_contents %>% filter(fish_id %in% fish$fish_id) %>% group_by(site) %>% summarise(S_ti = sum(count))
  dat <- sum_t %>% mutate(taxa = i)
  S_ti <- rbind.data.frame(S_ti, dat)
}

#calculate %Pi

S_i <- S_i %>% 
  mutate(site_taxa = paste(site, taxa, sep = "_"))

S_ti <- S_ti %>% 
  mutate(site_taxa = paste(site, taxa, sep = "_"))

P_i <- S_i %>% 
  full_join(S_ti) %>% 
  select(site, taxa, zone_trophic, S_i, S_ti) %>% 
  mutate(P_i = ((S_i/S_ti)*100))

amundsen <- F_i %>% 
  full_join(P_i)

amundsen$site <- factor(amundsen$site, levels = c("Percos", "Refugio", "R Beach"))
amundsen$zone_trophic <- factor(amundsen$zone_trophic, levels = c("Beach kelp associated", "Beach suspension feeder", "Other beach", "Marine kelp associated", "Marine suspension feeder", "Other marine"))

# break out sites

perc_amundsen <- amundsen %>% 
  filter(site == "Percos")

refu_amundsen <- amundsen %>% 
  filter(site == "Refugio")

rb_amundsen <- amundsen %>% 
  filter(site == "R Beach")

gut_contents_site_summary <- gut_contents %>% 
  filter(count>0) %>% 
  group_by(site) %>% 
  summarise(n_distinct(fish_id))

gut_contents_site_summary %>% 
  kbl() %>% 
  kable_styling()
```


```{r, fig.width=10}

#  geom_text(check.overlap = TRUE) 

ggplot(perc_amundsen, aes(x = F_i, y = P_i, label=taxa)) +
  geom_point(size = 3, 
             aes(color=zone_trophic, shape=zone_trophic)) +
  facet_wrap(~site) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", y = "% Prey-specific abundance") +
  scale_color_manual(values =  c("#C1C23C", "#C1C23C", "#0A6473", "#0A6473", "#C1C23C", "#0A6473")) +
  scale_shape_manual(values = c(16, 17, 16, 17, 3, 3))  +
  theme(panel.border = element_rect(fill = NA), 
        plot.title = element_text(size = 8))+
   geom_text(check.overlap = TRUE) 
  

ggplot(refu_amundsen, aes(x = F_i, y = P_i, label=taxa)) +
  geom_point(size = 3, 
             aes(color=zone_trophic, shape=zone_trophic)) +
  facet_wrap(~site) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", y = "% Prey-specific abundance") +
  scale_color_manual(values =  c("#C1C23C", "#C1C23C", "#0A6473", "#0A6473", "#C1C23C", "#0A6473")) +
  scale_shape_manual(values = c(16, 17, 16, 17, 3, 3))  +
  theme(panel.border = element_rect(fill = NA), 
        plot.title = element_text(size = 8))+
   geom_text(check.overlap = TRUE) 

ggplot(rb_amundsen, aes(x = F_i, y = P_i, label=taxa)) +
  geom_point(size = 3, 
             aes(color=zone_trophic, shape=zone_trophic)) +
  facet_wrap(~site) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", y = "% Prey-specific abundance") +
  scale_color_manual(values =  c("#C1C23C", "#C1C23C", "#0A6473", "#0A6473", "#C1C23C", "#0A6473")) +
  scale_shape_manual(values = c(16, 17, 16, 17, 3, 3)) +
  theme(panel.border = element_rect(fill = NA), 
        panel.grid = element_blank(), 
        plot.title = element_text(size = 8))+
   geom_text(check.overlap = TRUE) 

ggplot(amundsen, aes(x = F_i, y = P_i, label = taxa)) +
  geom_point(size = 3, 
             aes(color=zone_trophic, shape=zone_trophic)) +
  facet_wrap(~site) +
  theme_minimal() +
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  scale_y_continuous(limits = c(0, 100), breaks = c(0, 50, 100)) +
  coord_fixed(ratio = 1) +
  labs(x = "% Frequency of occurrence", 
       y = "% Prey-specific abundance"
       ) +
  scale_color_manual(values =  c("#C1C23C", "#C1C23C", "#C1C23C", "#0A6473", "#0A6473", "#0A6473")) +
  scale_shape_manual(values = c(16, 17, 3, 16, 17, 3))  +
  theme(panel.border = element_rect(size = .05, fill = NA), 
        panel.grid = element_blank(), 
        strip.text = element_text(size = 12), 
        legend.title = element_blank())
  
```

### SCA: Emerita

```{r}

emerita_gut_counts <- gut_contents %>% 
  filter(id == "Emerita analoga") %>% 
  group_by(site, season) %>% 
  summarise(total = sum(count), 
            sample_size = n())

#calculate average % abundance

gut_totals <- gut_contents %>% 
  group_by(fish_id) %>% 
  summarise(total_gut_content = sum(count))

percent_abund <- gut_contents %>% 
  full_join(gut_totals) %>%
  mutate(percent_abundance = (count/total_gut_content)*100) 

percent_abund_emerita <- gut_contents %>% 
  full_join(gut_totals) %>% 
  filter(id == "Emerita analoga") %>% 
  mutate(percent_abundance = (count/total_gut_content)*100) 

avg_percent_abund_emerita <- percent_abund_emerita %>% 
  group_by(site) %>% 
  summarise(avg = mean(percent_abundance), 
            se = sd(percent_abundance)/sqrt(n()), 
            n_guts = n())

ggplot(percent_abund, aes(x = site, y = percent_abundance, color = zone)) +
  geom_boxplot() +
    theme_minimal()
```

#### Emerita size vs. fish size

```{r}
seine_data <- read_xlsx(here("data", "Diet_seasonal_seine_data_raw.xlsx"), na = "NA") %>% 
  clean_names() %>% 
  subset(select = -c(30:61))

barred <- seine_data %>% 
  mutate(site_code = case_when(
    site == "Percos" ~ 1, 
    site == "Refugio" ~ 2, 
    site == "R Beach" ~ 3)) %>% 
  mutate(fish_id = paste(site_code, date, sample_number, sep = "_")) %>%  #Create unique fish id code in each data set
  mutate(month = month(date)) %>% 
  mutate(season = case_when(
    month == 6 ~ "Summer", 
    month == 7 ~ "Summer", 
    month == 8 ~ "Summer", 
    month == 9 ~ "Fall", 
    month == 10 ~ "Fall", 
    month == 11 ~ "Fall", 
    month == 12 ~ "Winter", 
    month == 1 ~ "Winter", 
    month == 2 ~ "Winter", 
    month == 3 ~ "Spring",
    month == 4 ~ "Spring",
    month == 5 ~ "Spring"
  )) %>%  #adds in column for season
  mutate(lifestage = ifelse(sl_mm >= 130, "Adult", "Juvenile")) %>%   #Adds column for life stage contingent on standard length
  filter(sp_code == "AMAR") %>% 
  filter(gut_collected == "Yes") %>% 
  filter(site %in% c("Percos", "Refugio", "R Beach")) %>% 
  filter(lifestage %in% c("Adult", "Juvenile")) %>% 
  filter(season %in% c("Summer", "Fall"))

prey_size_data <- read_xlsx(here("data", "Diet_gutcontent_size_data_raw.xlsx"), na = "NA") %>% 
  clean_names()

emerita_ingested <- prey_size_data %>% 
  filter(category == "Emerita analoga") %>% 
  filter(site %in% c("Percos", "Refugio", "R Beach")) %>% 
  mutate(site_code = case_when(
    site == "Percos" ~ 1, 
    site == "Refugio" ~ 2, 
    site == "R Beach" ~ 3
  )) %>% 
  mutate(fish_id = paste(site_code, date, fish_id, sep = "_")) %>% 
  left_join(barred, by=c("site", "date", "fish_id"))

```

```{r, fig.width=10}
ggplot(emerita_ingested, aes(x = size_mm, fill=sl_mm, group =sl_mm)) +
  geom_histogram() +
  theme_minimal() +
  xlim(0, 25) +
  scale_fill_gradient(high = "#657A85", low = "grey") +
  xlab("Ingested sand crab size (mm)") +
  ylab("Count") +
  labs(fill="Barred surfperch standard length (mm)") +
  theme(legend.position = c(.8, .75))
  

ggplot(emerita_ingested, aes(x = sl_mm, fill=size_mm, group =size_mm)) +
  geom_histogram() +
  theme_minimal() +
  scale_fill_gradient(high = "#657A85", low = "#E8FDFF") +
  xlab("Barred surfperch standard length (mm)") +
  ylab("Count") +
  labs(fill="Ingested sand crab size (mm)") +
  theme(legend.position = c(.3, .75))

```

```{r, fig.width=10}
#plot ingested emerita by size of consuming fish

ggplot(emerita_ingested, aes(x = sl_mm, y = size_mm, color = site)) +
  geom_point() +
  theme_minimal() +
  xlab("Standard length of Barred surfperch consumer (mm)") +
  ylab("Size of ingested Emerita analoga (mm)")+
  scale_color_manual("legend", values = c("#6797AE", "#AFEF8A", "#F9F871")) 

ggplot(emerita_ingested, aes(x = sl_mm, y = size_mm, color = season)) +
  geom_point() +
  theme_minimal() +
  xlab("Standard length of Barred surfperch consumer (mm)") +
  ylab("Size of ingested Emerita analoga (mm)")+
  scale_color_manual("legend", values = c("#6797AE", "#AFEF8A", "#F9F871"))
```

```{r, fig.width=10}
# repeat above plots but with emerita count not sizes

ingested_emerita_count <- gut_contents %>% 
  filter(id == "Emerita analoga") %>% 
  group_by(site, sl_mm) %>% 
  summarise(count = sum(count))

ggplot(ingested_emerita_count, aes(x = sl_mm, y = count, color = site)) +
  geom_point(size = 2) +
  theme_minimal() +
  xlab("Standard length of Barred surfperch consumer (mm)") +
  ylab("Number of Emerita analoga observed in gut")+
  scale_color_manual("legend", values = c("#6797AE", "#AFEF8A", "#F9F871"))

ingested_emerita_count_season <- gut_contents %>% 
  filter(id == "Emerita analoga") %>% 
  group_by(season, sl_mm) %>% 
  summarise(count = sum(count))

ggplot(ingested_emerita_count_season, aes(x = sl_mm, y = count, color = season)) +
  geom_point() +
  theme_minimal() +
  xlab("Standard length of Barred surfperch consumer (mm)") +
  ylab("Number of Emerita analoga observed in gut")+
  scale_color_manual("legend", values = c("#657A85", "#9A6978", "#783300"))

#could think about using same length~weight conversion for this and plot biomass
```

#### Emerita population data

```{r, fig.width=10}
emerita_pop_data <- read_xlsx(here("data", "Diet_emerita_population_data_raw.xlsx"), na = "NA") %>% 
  clean_names() %>% 
  subset(select = -c(22:23)) %>%
  filter(taxa == "Emerita analoga") %>%   
  filter(site %in% c("Percos", "Refugio", "R Beach")) %>% 
  mutate(month = month(date)) %>% 
  mutate(season = case_when(
    month == 6 ~ "Summer", 
    month == 7 ~ "Summer", 
    month == 8 ~ "Summer", 
    month == 9 ~ "Fall", 
    month == 10 ~ "Fall", 
    month == 11 ~ "Fall", 
    month == 12 ~ "Winter", 
    month == 1 ~ "Winter", 
    month == 2 ~ "Winter", 
    month == 3 ~ "Spring",
    month == 4 ~ "Spring",
    month == 5 ~ "Spring"
  )) %>%   #adds in column for season
  filter(season %in% c("Summer", "Fall"))

perc_emerita <- emerita_pop_data %>% 
  filter(site == "Percos")
refu_emerita <- emerita_pop_data %>% 
  filter(site == "Refugio")
rb_emerita <- emerita_pop_data %>% 
  filter(site == "R Beach")

ggplot(emerita_pop_data, aes(x = width_length_mm)) +
  geom_histogram(binwidth = 1, 
                 fill = "#657A85") +
  theme_minimal() +
  xlim(0, 25) +
  facet_wrap(~site)

ggplot(perc_emerita, 
       aes(x = width_length_mm)) +
  geom_histogram(binwidth = 1, 
                 fill = "#657A85") +
  labs(x = "Emerita size (mm)", y = "Count", title = "Percos") +
  theme_minimal() +
  facet_wrap(~season)
ggplot(refu_emerita, aes(x = width_length_mm)) +
  geom_histogram(binwidth = 1, 
                 fill = "#657A85") +
  labs(x = "Emerita size (mm)", y = "Count", title = "Refugio") +
  theme_minimal() +
  facet_wrap(~season)
ggplot(rb_emerita, aes(x = width_length_mm)) +
  geom_histogram(binwidth = 1, 
                 fill = "#657A85") +
  labs(x = "Emerita size (mm)", y = "Count", title = "R Beach") +
  theme_minimal() +
  facet_wrap(~season)
```

```{r}
#2 sample t-test of all emerita data aggregated

ingested_sizes <- emerita_ingested %>% 
  pull(size_mm)

pop_sizes <- emerita_pop_data %>% 
  pull(width_length_mm)

emerita_ttest <- t.test(x = ingested_sizes, y = pop_sizes)
```

### Exploratory data analysis

#### Max crab size vs. fish size

OLS regression on max sand crab size in fish of each size

```{r}
emerita_max <- emerita_ingested %>% 
  group_by(sl_mm) %>% 
  summarise(max_size = max(size_mm))

ggplot(emerita_max, aes(x = sl_mm, y = max_size)) +
  geom_point()

```

```{r}
emerita_lm <- lm(sl_mm ~ max_size, data = emerita_max)

emerita_lm_tidy <- tidy(emerita_lm)

plot(emerita_lm)

emerita_cor <- cor.test(emerita_ingested$sl_mm, emerita_ingested$size_mm)

```

#### Gut content richness

- calculate index of diversity from each gut
- run an anova to compare by site

```{r}
gut_richness <- gut_contents %>% 
  group_by(site, season, fish_id) %>% 
  summarise(richness = n_distinct(diversity))

avg_gut_richness <- gut_richness %>% 
  group_by(site) %>% 
  summarise(avg_richness = mean(richness), 
            se = sd(richness)/sqrt(n()), 
            n_guts = n(), 
            var(richness))

ggplot(avg_gut_richness, aes(x = reorder(site, -avg_richness), y = avg_richness, fill = site)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymax = avg_richness+se, 
                    ymin = avg_richness-se), 
                width = 0.1, 
                position = position_dodge(.9)) +
    theme_minimal() + 
  scale_fill_manual("legend", values = c("#657A85", "#CB7F2A", "#BBA5B7")) +
  ylab("Average # taxa in Barred surfperch stomachs") +
  xlab("") +
  theme(legend.position = "none")

```
ANOVA assumptions

```{r}
#normality of data: questionable. Looks very much right skewed

ggplot(gut_richness, aes(x = richness)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~site)

ggplot(gut_richness, aes(x = site, y = richness)) +
  geom_boxplot()

#equal variance: not significant, we retain the null hypothesis of equal variance

leveneTest(richness ~ site, data = gut_richness)
```

One-way ANOVA

```{r}
richness_aov <- aov(richness ~ site, data = gut_richness)
summary(richness_aov)

richness_lm <- lm(richness ~ site, data = gut_richness)
richness_aov_t3 <- Anova(richness_lm)
richness_aov_t3

TukeyHSD(richness_aov)

#R Beach and Refugio were statistically sig. different, others not
```
Conclusion: Gut richness differed significantly between Refugio (mean +/- se) and R Beach (mean +/- se) Barred surfperch stomach contents (one-way ANOVA with post-hoc Tukey's HSD, F(df) = 3.14, *p* < 0.05). 


#### Emerita vs Donax prey items


```{r}
emerita_gut_counts <- gut_contents %>% 
  select(site, date, season, fish_id, sl_mm, lifestage, taxa, count) %>% 
  complete(nesting(site, date, season, fish_id, sl_mm, lifestage), taxa, fill=list(count=0)) %>% 
  filter(taxa == "Sand crab")

ggplot(emerita_gut_counts, aes(x = count)) +
  geom_histogram() +
  facet_wrap(~site)

donax_gut_counts <- gut_contents %>% 
  select(site, date, season, fish_id, sl_mm, lifestage, taxa, count) %>% 
  complete(nesting(site, date, season, fish_id, sl_mm, lifestage), taxa, fill=list(count=0)) %>% 
  filter(taxa == "Bean clam")

ggplot(donax_gut_counts, aes(x = count)) +
  geom_histogram() +
  facet_wrap(~site)

```